%
\usemodule[ctx-thesis-v0.993]
\usemodule[bib.sty-v2.78]
\usemodule[vim]

\setupthesis[en+sk,mendelu,pef,none][	% language,university,faculty,department
  type={dp},             % bp=bachelor, dp=diploma, pp=PhD, zp=final thesis,  sp=seminar work,  pr=protocol/report, pt=project, doc=documentation; for more abbreviations, see the Documentation.
  authorname={Damián},	 % your name
  authorsurname={Sova},  % your surname
  authordegree={Bc.},	   % your academic degree
  % authorgender={M},     % M=male, F=female; not necessary for English
  supervisor={doc. Ing. Oldřich Trenz, Ph.D.},  % name, surname and degree of your thesis supervisor
  titleen={Automated neural network learning for higher accuracy human skeleton detection under realistic conditions}, 	               % title in English
  title={Automatizované učenie neurónových sietí na presnejšiu detekciu ľudskej kostry v~reálnych podmienkach},                           % title in the second language
  keywordsen={pose estimation, human skeleton detection, data generation},
  keywords={odhadovanie pózy, detekcia ľudskej kostry, generovanie dát},
  acknowledgement={I express my sincere gratitude to my supervisor, Doc. Ing. Oldřich Trenz, Ph.D., for his invaluable time, unwavering support, and insightful guidance throughout the entirety of this research journey. I~am also deeply appreciative of the expert consultations provided by RNDr. Michal Procházka, Ph.D., from visioncraft s.r.o., whose regular insights played a pivotal role in shaping the trajectory of this work. Lastly, heartfelt thanks to my friends and family for their unwavering support, encouragement, and understanding, without which this endeavor would not have been possible.},
  abstracten={Recent advancements in computer vision have led to the widespread adoption of neural networks for human pose estimation, yet challenges persist in applying these technologies to real-world scenarios. While accuracy on benchmark datasets continues to improve, many existing datasets fail to capture the complexities encountered in practical applications, such as individuals at varying distances from the camera, crowded environments, and heavily occluded scenes. Consequently, models trained on such datasets often exhibit significant underperformance when deployed in real-world settings. This thesis introduces a novel Unified Format approach to address these challenges by standardizing the aggregation of outputs from diverse neural network models. By unifying the outputs of models like MoveNet, PoseNet, and MMPose into a cohesive structure, the Unified Format facilitates the creation of customized datasets tailored to real-world conditions.

  The Unified Formats performance evaluation reveals promising results, particularly in metrics such as Average Percentage Error (APE) and Mean Squared Error (MSE), which indicate close alignment between predicted and ground-truth keypoints. However, challenges arise with the Object Keypoint Similarity (OKS) metric due to stringent evaluation criteria and prediction discrepancies among models. The low OKS metric values stem from prioritizing detection models for simplicity and speed over precision. Using more accurate models tailored for dataset creation could significantly improve OKS scores in real-world scenarios. Nonetheless, the Unified Format performs satisfactorily in accurately localizing keypoints, especially compared to individual model outputs.

  In summary, while this thesis does not present evidence of substantial improvement over existing benchmark performances, it successfully addresses the challenges associated with human pose estimation dataset creation by proposing and implementing a Unified Format. The format facilitates the aggregation of outputs from multiple neural network models, streamlining the dataset generation process. Despite remaining challenges, continued refinement and exploration of techniques offer opportunities to improve the Unified Format further and advance the field of human pose estimation.},		 % abstract in English
  abstract={Nedávne pokroky v oblasti počítačového videnia viedli k rozsiahlemu prijatiu neurónových sietí pre odhad ľudskej pózy, avšak výzvy pretrvávajú pri aplikácii týchto technológií v reálnych scenároch. Zatiaľ čo sa presnosť na benchmarkových datasetoch stále zlepšuje, mnohé existujúce datasety nedokážu zachytiť zložitosť, s ktorou sa stretávame v praktických aplikáciách. Ako sú napríklad jednotlivci v rôznych vzdialenostiach od kamery, preplnené prostredia a scény z ťažkým prekrývaním. V dôsledku toho modely trénované na takýchto datasetoch často prejavujú výrazný nedostatok výkonu pri nasadení v reálnych prostrediach. Táto práca uvádza nový prístup Zjednotený Formát na riešenie týchto výziev prostredníctvom štandardizácie agregácie výstupov z rôznych modelov neurónových sietí. Zjednocovaním výstupov modelov ako MoveNet, PoseNet a MMPose do koherentnej štruktúry umožňuje Zjednotený Formát vytváranie špecifických datasetov prispôsobených reálnym podmienkam.

  Hodnotenie výkonu Zjednoteného Formátu odhalilo sľubné výsledky, najmä v metrikách ako Priemerná Percentuálna Chyba (APE) a Priemerná Štvorcová Chyba (MSE), ktoré naznačujú výraznú blízkosť medzi predpovedanými a skutočnými kľúčovými bodmi osôb na obraze. Avšak, výzvy vznikajú s metrikou Podobnosti Kľúčových Bodov Objektu (OKS) kvôli prísnym evaluačným kritériám a rozdieľom predikcií medzi použitými modelmi. Nízke hodnoty metriky OKS vychádzajú z aplikovania detekčných modelov zameraných na jednoduchosť a rýchlosť oproti presnosti. Použitie presnejších modelov prispôsobených na presnosť detekcie by významne zlepšilo skóre OKS v reálnych scenároch. Napriek tomu Zjednotený Formát uspokojivo funguje pri lokalizovaní kľúčových bodov.

  Táto práca nepredstavuje dôkazy o významnom zlepšení oproti existujúcim výkonom benchmarkov, úspešne však rieši výzvy spojené s tvorbou datasetov na odhad ľudskej pózy prostredníctvom navrhovania a implementácie Unified Formátu. Tento prístup umožňuje agregáciu výstupov z viacerých modelov neurónových sietí, zjednodušujúc proces generovania datasetov. Napriek prítomným výzvam existujú ďalšie možnosti na zdokonalenie a preskúmanie techník pre zlepšenie Unified Formátu, ktoré môžu posunúž oblast odhadu ľudskej pózy vpred.},		   % abstract in the second language
  % abstracten={},		 % abstract in English
  location={Brno},	 % location
%  year={2021},		   % year, the default is the current year
 thesisassignmentform={assignment/diploma-thesis-topic-1.pdf,assignment/diploma-thesis-topic-2.pdf},  % file(s) with thesis assignment
]

\setupinteraction[state=start]
% \setupinteraction[color=black,style=bold]
\startthesis
\startbodymatter

% Preparing language highlighting used for source code
\setuptyping[]
\definevimtyping
[PY]
[
  syntax=python,
  tab=3,
  numbering=yes,
  style={\setupbodyfont[mono,9dd]},
]

\setuptyping[]
\definevimtyping
[BA]
[
  syntax=bash,
  tab=3,
  numbering=yes,
  style={\setupbodyfont[mono,9dd]},
]

\setuptyping[]
\definevimtyping
[JSON]
[
  syntax=json,
  tab=3,
  numbering=yes,
  style={\setupbodyfont[mono,9dd]},
]

% Source codes
\input{source-codes/data-types}
\input{source-codes/detection-script-backbone}
\input{source-codes/detection-script-frame}
\input{source-codes/detection-script-output}
\input{source-codes/unification-script-call}
\input{source-codes/unification-script-main}
\input{source-codes/unified-format}
\input{source-codes/unified-format-output}
\input{source-codes/skeleton-file}
\input{source-codes/euclidean-distance}
\input{source-codes/oks-k-values}

% Chapters

\input{chapters/abbreviations}

\input{chapters/introduction}

\input{chapters/theoretical_foundations}

\input{chapters/practical_part}

\input{chapters/conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%% \def\refname{}

\input{references/sources}

\stopbodymatter

%%%%%%%%%%%%%%%%%%%%%%%% The variant where lists become as a part of the work and they are not put in Appendices.

\setupsectionblock[backmatter][before={\setuplist[kap][before={}]}]

\startbackmatter

\THESIScompletelistof{tables}
\THESIScompletelistof{figures}
\THESIScompletelistof{abbreviations}
\THESIScompletelistof{codes}

\stopbackmatter

%%%%%%%%%%%%%%%%%%%%%%%% The variant where lists does not become as a part of the work but they are put in Appendices.
%%%%%%%%%%%%%%%%%%%%%%%% For enabling the _following_ four commands, erase the percent sign.
%%%%%%%%%%%%%%%%%%%%%%%% Put the percent sign for disabling the _previous_ four commands.

\startappendices

\cast{Appendices}
%\THESIScompletelistof{tables}
%\THESIScompletelistof{figures}
%\THESIScompletelistof{abbreviations}
%\THESIScompletelistof{codes}

\stopappendices

\stopthesis

\endinput		

